### 2009-04-03 talk/icooolps2009-dotnet/clibackend.tex
describe what is a flexswitch and why it's useful to produce good code

However the concept of \emph{flexswitch}, as described in
Section~\ref{sec:implementing-promotion}, does not have any direct equivalent
in the CLI model, and it is hard to implement efficiently.

>>>>

However the concept of \emph{flexswitch}, as described in
Section~\ref{sec:jitgen}, does not have any direct equivalent
in the CLI model, and it is hard to implement efficiently.

### 2009-04-03 talk/icooolps2009-dotnet/intro.tex
describe what is a flexswitch and why it's useful to produce good code

\subsection{PyPy and JIT-Generation}

@@

@@

\anto{XXX: we need to explain what is a flexswitch!}

>>>>

\subsection{PyPy and JIT-Generation}
\label{sec:jitgen}

@@

Implementing such a behavior requires a tight coupling between compile-time
and run-time: a \emph{callback} is put in the generated code, which can invoke
the compiler again.  When the callback is actually reached at run-time, and
only then, the compiler resumes and uses the knowledge of the actual run-time
value to generate more code.

The new generated code is potentially different for each run-time value seen.
This implies that the generated code needs to contain some sort of updatable
switch, or \emph{flexswitch}, which can pick the right code path based on the
run-time value.  Typically, the value we switch on is the runtime dynamc type
of a value, so that the JIT compiler has all information needed to produce
very good code for that specific case.

@@
